Sparse Matrix Vector Multiplication with Multiple vectors and Multiple Matrices on the MIC Architecture

### 2013-10-18 ieee_paper.tex
removing todos

\begin{figure}
  \centering 
  \includegraphics[width=.9\linewidth]{figures/gflops_peak.pdf}\label{fig:gflops-peak-perf}
  \caption{Estimation of the maximum achievable performance using a
    device with a bandwidth from memory to computational units of 150~GB/s when
    varying the number of vectors and matrices.\todo{yabel=Peak Performance (Gflop/s)}\todo{no xlabel}}
  \label{fig:perf_predict}
\end{figure}

@@

  \caption{Bandwidth performance under idealized conditions.  Entries
    with "cpp" (triangles) denote cases where vectorization is
    compiler generated. \todo{legend} \todo{ylabel=Bandwidth(GB/s)}}
  \label{fig:bandwidth}
  \label{fig:band_rw_MIC}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=.9\linewidth]{figures/bandwidth_gather_unpack.pdf}
  \caption{Performance of gather and unpack operations.\todo{ylabel=Bandwidth(GB/s)}}
  \label{fig:band_gather} 
\end{figure}
%

@@

  \caption{Performance of the manually vectorized code. The two
    horizontal lines depict the worst and the best predicted performances. \todo{font size} \todo{ylabel=Performance(Gflop/s)}}
  \label{fig:expe_types}
\end{figure*}

@@

  \caption{Performance of $y=Ax$ for a RBF derivative stencil of a
    $96^3$ 3D grid. Classical SpMV ($n_m=n_v=1$ given in blue) has low
    performance. The manually vectorized code (red) is 3.5 times
    faster than the compiler generated one (green). RCM ordering
    (squares) only improves the performance for our manually
    vectorized code.\todo{ylabel=Performance(Gflop/s)}}
  \label{fig:comparison_spmv}
  \label{fig:perf_mic}
\end{figure}

>>>>

\begin{figure}
  \centering 
  \includegraphics[width=.9\linewidth]{figures/gflops_peak.pdf}\label{fig:gflops-peak-perf}
  \caption{Estimation of the maximum achievable performance using a
    device with a bandwidth from memory to computational units of 150~GB/s when
    varying the number of vectors and matrices.}
  \label{fig:perf_predict}
\end{figure}

@@

  \caption{Bandwidth performance under idealized conditions.  Entries
    with "cpp" (triangles) denote cases where vectorization is
    compiler generated.}
  \label{fig:bandwidth}
  \label{fig:band_rw_MIC}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=.9\linewidth]{figures/bandwidth_gather_unpack.pdf}
  \caption{Performance of {\tt gather} and {\tt unpack} operations.}
  \label{fig:band_gather} 
\end{figure}
%

@@

  \caption{Performance of the manually vectorized code. The two
    horizontal lines depict the worst and the best predicted performances. \todo{font size}}
  \label{fig:expe_types}
\end{figure*}

@@

  \caption{Performance of $y=Ax$ for a RBF derivative stencil of a
    $96^3$ 3D grid. Classical SpMV ($n_m=n_v=1$ given in blue) has low
    performance. The manually vectorized code (red) is 3.5 times
    faster than the compiler generated one (green). RCM ordering
    (squares) only improves the performance for our manually
    vectorized code.}
  \label{fig:comparison_spmv}
  \label{fig:perf_mic}
\end{figure}
